From Freebase to Wikidata: The Great Migration

### 2015-10-17 paper.tex
Formulation
minor

The first challenge concerns the licenses under which the datasets are published.
Wikidata is published under the Creative Commons~0 (CC0~1.0)~\cite{cc0} license,
which effectively puts the data in the public domain,
whereas Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license
and contains data imported from external projects not owned by Google,
like images or descriptions extracted from Wikipedia.
In consequence Google does not own the copyright of some parts of the content of the knowledge base,
such as images or long entity descriptions extracted from Wikipedia.
In a~first step, we filtered the Freebase dump for this kind of content
before being able to create a~data dump that we could relicense under CC0~1.0.
This step reduced the number of Freebase facts that could be republished by about 42M~facts
from 3~billion facts in the original corpus.

@@

The second challenge is that the Wikidata community is very eager to have references
for their statements, \emph{i.e.}, sources that Freebase usually did not store,
except for some specific data like populations and unemployment rates.
For these two specific cases, we have just kept the references from Freebase.
In order to provide the Wikidata community with references for the facts in Freebase,
we have reused data from another Google research project
called Knowledge Vault~\cite{dong2014knowledge} aimed at extracting facts from the Web.
Whereas the fact extraction was usually correct, the pages Knowledge Vault extracted
the references from often do not meet the Wikidata requirements for reliable references:
they include pages in social networks, shopping sites, file sharing hosters, \emph{etc.}
It became necessary to filter the references before potential inclusion in Wikidata
by introducing a~domain blacklist.%
\footnote{Domain blacklist:
\url{https://www.wikidata.org/wiki/Wikidata:Primary_sources_tool/URL_blacklist}}

>>>>

The first challenge concerns the licenses under which the datasets are published.
Wikidata is published under the Creative Commons~0 (CC0~1.0)~\cite{cc0} license,
which effectively puts the data into the public domain.
Freebase is published under a~Creative Commons Attribution (CC~BY~2.5) license.
Google does not own the copyright of some parts of the content of the knowledge base,
such as images or long entity descriptions extracted from Wikipedia.

We filtered the Freebase dump by removing this kind of content
before creating a~data dump that Google could relicense under CC0.
This step reduced the number of Freebase facts that could be republished by about 42 million facts
from 3~billion facts in the original corpus, i.e. by about $1.4\%$.

@@

The second challenge is that the Wikidata community is very eager to have references
for their statements, \emph{i.e.}, sources that Freebase usually did not store,
except for some specific data like populations and unemployment rates.
For these two specific cases, we have just kept the references from Freebase.
\todo{Thomas, can you expand?}

In order to provide the Wikidata community with references for the facts in Freebase,
we have reused data from the Google
Knowledge Vault~\cite{dong2014knowledge}. Knowledge Vault aims at extracting facts from the Web.

The result of this step was surprising: 
the fact extraction was usually correct, in the sense that the fact was indeed being stated on the page.
Also the fact itself was usually accurate, in the sense that it corresponded to reality.
But the pages the facts were extracted from in many cases did not meet
the Wikidata requirements for reliable references:
they include pages in social networks, reviews on shopping sites, file sharing hosters, \emph{etc.}
It became necessary to filter the references before potential inclusion in Wikidata
by introducing a~domain blacklist.%
\footnote{Domain blacklist:
\url{https://www.wikidata.org/wiki/Wikidata:Primary_sources_tool/URL_blacklist}}
